---
title: "**My Web-CV**" 
output:
  html_document:
    theme: cosmo
output_dir: "."
---


<style>
body {
text-align: justify}

.nav>li>a {
    position: relative;
    display: block;
    padding: 10px 15px;
    color: #990000;
}
.nav-pills>li.active>a, .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus {
    color: #ffffff;
    background-color: #990000;
}

a:link {
  color: #990000;
  background-color: transparent;
  text-decoration: none;
}

a:visited {
  color: pink;
  background-color: transparent;
  text-decoration: none;
}

a:hover {
  color: darkblue;
  background-color: transparent;
  text-decoration: underline;
}

a:active {
  color: yellow;
  background-color: transparent;
  text-decoration: underline;
}

</style>

### *Welcome to my online CV* {.tabset .tabset-fade .tabset-pills}


#### What this webpage is about {.tabset}
* With this webpage I would like to express my sincere interest in the position as a **working student** in the      department **market analytics** at Sony Music. Here I have provided everything for you in order to get to know me   a little better and get an idea what my motivation is. You can find out where my passion for data science      derives from and what made me aspire to become to a Data Scientist. If you would like to jump directly to a    quick overview, click <a href="https://fabio-auerswald.github.io/Resume.html "rel="noopener noreferrer" target="_parent">here</a>.

#### What can be found on this webpage {.tabset}
* A Resume, with detailed information about my education, work experience and further skills
* A section with more details and an introduction
* References to my musical activities
* Contact info


#### How this webpage was created {.tabset}
* This webpage was build with RStudio using the documentation tool RMarkdown including html, css and Github      Pages for publishing it on the web.





```{r, echo=FALSE, include=FALSE, warning=FALSE }

if (!require("pacman")) install.packages("pacman")
pacman::p_load("tidyverse", "viridis", "ggplot", "hrbrthemes")

setwd("/Users/Fabio/Desktop/GitHub/Fabio-Auerswald.github.io")
students <- readxl::read_excel("/Users/Fabio/Desktop/GitHub/Fabio-Auerswald.github.io/students.xlsx")

violin <- ggplot(students, aes(y=age, x=faculty, fill=faculty)) +
  
  geom_violin(position="dodge") +
  
  geom_boxplot(width=0.2) +
  
  labs(title = "Violin plot",
       
       fill = "Faculty",
       
       subtitle = "Distribution of student age by faculty",
       
       caption = "Fabio Auerswald, 2022",
       legend_title = "Figure") +
  
  ylab("Respondents's age (in years)") +
  xlab("Faculty") + 
  
  scale_y_continuous(limits= c(0,65)) +
  
  theme_light()

```


<br/><br/>

# .

## *Violin Plot with sample data*

* Following figure shows a violin plot showing a age distribution sorted by faculty.

```{r, echo=FALSE, warning=FALSE, fig.align='center' }
violin
```