---
title: "**References**"
output:
  html_document: 
    number_sections: false
    toc: true
    toc_depht: 3
    toc_float: true
    collapsed: true
output_dir: "."
---

<style>
a:link {
  color: #990000;
  background-color: transparent;
  text-decoration: none;
}

a:visited {
  color: pink;
  background-color: transparent;
  text-decoration: none;
}

a:hover {
  color: red;
  background-color: transparent;
  text-decoration: underline;
}

a:active {
  color: yellow;
  background-color: transparent;
  text-decoration: underline;
}

.nav>li>a {
    position: relative;
    display: block;
    padding: 10px 15px;
    color: #990000;
}
.nav-pills>li.active>a, .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus {
    color: #ffffff;
    background-color: #990000;
}
</style>

## *Music Projects*

#### <a href="https://www.youtube.com/watch?v=EjZedUpnmVI&t=2041s" target="_blank">The N.E.R.D. Expereince Part 1 celebrated by the GEEKx</a>
* The Geekx is a project I participated in to celebrate the music of  N.E.R.D.


#### <a href="https://youtu.be/GLKWujRzgxk?t=1484" target="_blank">Secric Perry Live | CURL CON Virtual</a>
* Sedric Perry is a Berlin based artist whom I performed with on several occasions. Here is one of them.


## *Music Professors*
#### <a href="https://www.musiktheorie-komposition.de/referenzen" target="_blank">Carlo Inderhees</a>
* Carlo Inderhees is a teacher of music theory with over 25 years of experience. I took lessons with Carlo in the areas of composition, harmony and rhythm.

#### <a href="https://www.corneliusclaudiokreusch.com/CCK.html" target="_blank">Cornelius C. Kreusch</a> 
* Cornelius C. Kreusch is a german pianist who is well known in the jazz-scene and has played with jazz legends such as Herbie Hancock, Bobby McFerrin, Jaky Byard and many more. He has been an inspiring source for my playing and musical development. 

<br/><br/>

## *One of my Favorite Songs*

```{=html}
<iframe src="https://open.spotify.com/embed/track/4MIPpjKWw1lLVwS6tLhis1?utm_source=generator" width="100%" height="80" frameBorder="0" allowfullscreen="" allow="autoplay; clipboard-write; encrypted-media; fullscreen; picture-in-picture"></iframe>
```

<br/><br/>

## *Data Visualisation Examples* {.tabset .tabset-fade .tabset-pills}

### Hisogram Chart {.tabset}
* The following bar-chart shows the five most used keys of my favorite pianist Ahmad Jamal. The data is downloaded via an API from my most used streaming platform.

```{r, echo=FALSE, include=FALSE, warning=FALSE, message=FALSE}

# Loading required packages
library(spotifyr)
library(tidyverse)
library(httpuv)
library(knitr)
library(devtools)
library(dplyr)

# Connect to Spotify API
Sys.setenv(SPOTIFY_CLIENT_ID = "9af1a624b5da4e199e8782f6cf806378")
Sys.setenv(SPOTIFY_CLIENT_SECRET = "2db3f175820f43248d4bcf0dcd6580a5")

access_token <- get_spotify_access_token()



ahmad_jamal <- get_artist_audio_features('ahmad jamal')

## Selecting only the wanted columns
ahmad_jamal_1 <- ahmad_jamal %>% dplyr::select(key_mode, key, key_name)

## What were Ahmad Jamals favorite keys to play in?
ahmad_jamal_favorite <- ahmad_jamal %>% 
  count(key_mode, sort = TRUE) %>% 
  head(5) 

ahmad_jamal_favorite <- as.data.frame(ahmad_jamal_favorite)

favourite <- as.data.frame(ahmad_jamal_favorite) %>% 
  
  ggplot(aes(x=key_mode, y=n, fill=key_mode)) +
  
  geom_bar(stat="identity")   + 
  geom_text(aes(label=key_mode), hjust=2) +
  coord_flip() +
  
  labs(title ="",
       caption = "Fabio Auerswald, 2022",
       subtitle = "Ahmad Jamal's favorite keys to play in ",
       fill = "Favorite Key") +
  
  xlab("") +
  ylab("Number of songs composed in this key")  +
  theme_light() +
  
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

```


```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center' }
favourite

```




### Violin Plot {.tabset}
* Following figure shows a violin plot including a boxplot showing the age distribution sorted by faculty. The used data originates from a sample data-frame with information about students. 
```{r, echo=FALSE, include=FALSE, warning=FALSE }

if (!require("pacman")) install.packages("pacman")
pacman::p_load("tidyverse", "viridis", "ggplot", "hrbrthemes")

setwd("/Users/Fabio/Desktop/GitHub/Fabio-Auerswald.github.io")
students <- readxl::read_excel("/Users/Fabio/Desktop/GitHub/Fabio-Auerswald.github.io/students.xlsx")

violin <- ggplot(students, aes(y=age, x=faculty, fill=faculty)) +
  
  geom_violin(position="dodge") +
  
  geom_boxplot(width=0.2) +
  
  labs(title = "Violin plot",
       
       fill = "Faculty",
       
       subtitle = "Distribution of student age by faculty",
       
       caption = "Fabio Auerswald, 2022",
       legend_title = "Figure") +
  
  ylab("Respondents's age (in years)") +
  xlab("Faculty") + 
  
  scale_y_continuous(limits= c(0,65)) +
  
  theme_light()

```

```{r, echo=FALSE, warning=FALSE, fig.align='center' }
violin
```


### Ridgeline Plot {.tabset}
* Here you can see the R code of a quick data wrangling process with a final data visualization in a ridge-line plot. The plot shows the liking distribution by course of all students from the same data-frame as used before.

``` {r, echo=TRUE, include=TRUE, warning=FALSE, message=FALSE}

# Automized loading of all packages at once
if (!require("pacman")) install.packages("pacman")
pacman::p_load("tidyverse", "viridis", "ggridges", "hrbrthemes")

# Setting a working directory and loading data
setwd("/Users/Fabio/Desktop/GitHub/Fabio-Auerswald.github.io")
students <- readxl::read_excel("/Users/Fabio/Desktop/GitHub/Fabio-Auerswald.github.io/students.xlsx")

# Data wrangling followed by the visualization of desired information
ridge <-  students %>%
  mutate(like= as.numeric(like),
         course = as.factor(course)) %>%
  filter(!is.na(course), !is.na(like)) %>%
  ggplot(aes(x = like, y = reorder(course, like), fill = ..x..)) +
  geom_density_ridges_gradient(scale = 3, rel_min_height = 0.01) +
  scale_fill_viridis() +
  labs(title = "How much students like their course?") +
  xlab("Liking the course (1-6)") +
  ylab("Course enrollment") +
  theme_ipsum() +
  theme(
    legend.position="none",
    panel.spacing = unit(0.1, "lines"),
    strip.text.x = element_text(size = 8)
  )
```

```{r figure,  echo=FALSE, warning=FALSE, message=FALSE, fig.align='center'}

ridge

```
