---
title: "**Resume**" 
output:
  html_document: 
    number_sections: false
    toc: true
    toc_depht: 2
    toc_float: true
    collapsed: true
output_dir: "."
---

<style>
body {
text-align: justify}

.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    z-index: 2;
    color: #fff;
    background-color: #990000;
    border-color: transparent;
}

.nav>li>a {
    position: relative;
    display: block;
    padding: 10px 15px;
    color: #990000;
}
.nav-pills>li.active>a, .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus {
    color: #ffffff;
    background-color: #990000;
}
</style>


	
```{css, echo = F}
img {
    float: right;
}
```


```{css, echo = F}
ul {
    color: #990000;
}
```

* Click <a id="raw-url" href="https://github.com/Fabio-Auerswald/Fabio-Auerswald.github.io/raw/main/Fabio-Auerswald-Resume.pdf">here</a> if you would like to download this resume as a pdf file.


## *EDUCATION*

#### **Bachelor’s degree at the University of Potsdam**

  * *10/ 2019 – Present | Economics with sociology as a supplementary subject* 
      + Majors: Mathematics, Econometrics & organizational sociology
      
<br/>


#### **Music studies**
  - *02/2019-09/2019 | Self-organized study in jazz piano*
    + Lessons by two faculty members: Carlo Inderhees & Cornelisu C. Kreusch 
    + Lessons in the areas of composition, harmony, rhythm, classical music, and jazz
    
<br/>


#### **Bachelor’s degree at HTW Berlin**
 - *04/2017-01/2019 | Degree in Mechanical engineering*
    + Majors: mathematics, & computer science
    + Semester abroad at the Universidade Federal de Mina Gerais in Belo Horizonte, Brazil
    
<br/>


#### **Language course in Buenos Aires, Argentina**
  - *05/ 2015 – 04/ 2016 | Intensive language course in Academia Buenos Aires*
    + Attained language proficiency A1 till C1
    
<br/>
    
    
#### **Vocational training at MTU Friedrichshafen GmbH**
  - *09/ 2011 – 08/ 2014 | Industrial mechanic training & acquired entrance qualification for the university of applied sciences*
    + Dual vocational training in metal technology at Claude-Dornier-Schule 
    
<br/><br/>


## *WORK EXPERIENCE*

#### **New Beings**
  - *10/ 2021 – Present | Facilitator for Project-related Workshops*
    + Interactive Workshops and presentations in companies regarding topics such as racism, diversity, and            inclusion
      
<br/>

#### **JAYJAY-Models**
  - *11/ 2016 – Present | Running contract with a modeling agency*
    + Actor for film and advertising campaigns in cooperation with companies such as Mercedes, BMW, LEVI‘s,         etc.

<br/>

#### **Rolls-Royce Power System AG**
  - *07/ 2014 – 04/ 2015 - Placement Industrial mechanic*
    + Work area: Locksmith & Quality control


<br/><br/>



## *LANGUAGES & SKILLS* {.tabset .tabset-fade .tabset-pills}


### Languages {.tabset}
```{r, echo=FALSE, include=FALSE, warning=FALSE }
if (!require("pacman")) install.packages("pacman")
pacman::p_load("tidyverse", "ggplot2")

language_skill <- as.data.frame(
  tibble(
    language = c("German", "English", "Portuguese", "Spanish", "French"),
    niveau = c("native", "C1", "B2", "C1","B1" ),
    level = c(7, 5, 4, 5, 3 )
  )
)

labels <- c("German", "English", "Portuguese", "Spanish", "French")

languages <- language_skill %>% ggplot(aes(x=language, y=as.numeric(level), fill=language)) +
  
  geom_bar(stat="identity")   + 
  geom_text(aes(label=labels), hjust=2.5) +
  coord_flip() +
  
  labs(title ="",
       caption = "Fabio Auerswald, 2022",
       subtitle = "Language levels according to the European Framework of Reference",
       fill = "Spoken Languages") +
  
  xlab("") +
  ylab("Language proficiency") +
  
  scale_y_discrete(name ="Levels", 
                   limits=c("A1","A2","B1","B2","C1","C2", "Native")) +
  theme_light() +
  
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

```


```{r echo=FALSE, warning=FALSE, fig.align='right'}

languages
```

### Skills

* MS-Office-
* R (Programming language)
  + RMarkdown (data reporting)
  + Rvest (web-scraping)
* STATA	
* HTML		
* CSS
* Python		
* PostgreSQL
* Econometrics




